---
title: "Yelp"
author: "Amr Attyah"
date: "1/13/2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Libraries
```{r message=FALSE}
library(rpart)				        # Popular decision tree algorithm
library(rpart.plot)			    	# Enhanced tree plots
library(RColorBrewer)			  	# Color selection for fancy tree plot
library(party)					      # Alternative decision tree algorithm
library(partykit)				      # Convert rpart object to BinaryTree
library(caret)					      # Just a data source for this script
library(e1071)
library(tree)
library(data.table)
library(ggplot2)
library(gridExtra)
library(plyr)
```


## Loading Yelp Dataselt
Dataset can be found here see <https://www.kaggle.com/yelp-dataset/yelp-dataset/data>.
```{r}
# load
training.x<-read.csv("training.x.csv")
training.x<-training.x[,-19]
training.y<-read.csv("training.y.csv")
testing.x<-read.csv("testing.x.csv")
testing.x<- testing.x[,-19]
testing.y<- read.csv("testing.y.csv")


```

## Cleaning The Dataset
```{r}
cnvrt.factor <- c(2:16)
training.x<-subset(training.x, select = -c(X))
training.x[,cnvrt.factor]<- lapply(training.x[,cnvrt.factor], factor)
training.y<-subset(training.y, select = -c(X))
training.y<- as.factor(training.y$x)
testing.x<-subset(testing.x, select = -c(X))
testing.x[,cnvrt.factor]<- lapply(testing.x[,cnvrt.factor] , factor)
testing.y<-subset(testing.y, select = -c(X))
testing.y<- as.factor(testing.y$x)

training<- cbind(training.x,training.y)

```

## Model Tuning
Traing a Classfication Tree Model having the with 10 fold cross validation method

```{r}

train_control<- trainControl(method="cv", number=10)



clasmodel<- train(x=training.x, y=training.y, trControl=train_control, method="rpart")
clasmodel
plot(clasmodel)
```


# Model Validation

```{r}
tree.pred<- predict(clasmodel, testing.x)
testResultsTREE <- data.frame(obs = testing.y, pred = tree.pred)
tree.summary<-defaultSummary(testResultsTREE)
cm.tree2<-confusionMatrix(tree.pred,testing.y, positive = "Good")
cm.tree2
```

# Model Validation using ROC
```{r}
# ROC

# convert good to 1, bad to 0
goodbad<- function(x){
        if (x=="Good"){
                return(1)
        }
        else{
                return(0)
        }
}
test.converted<-sapply(testResultsTREE$obs,goodbad) 
pred.converted<-sapply(testResultsTREE$pred,goodbad)

library(ROCR)

tree_scores <- prediction(pred.converted, test.converted)

#ROC Curve
tree_perf <- performance(tree_scores, "tpr", "fpr")

plot(tree_perf,
     main="classification tree ROC Curves",
     xlab="1 - Specificity: False Positive Rate",
     ylab="Sensitivity: True Positive Rate",
     col="darkblue",  lwd = 3)
abline(0,1, lty = 300, col = "green",  lwd = 3)
grid(col="aquamarine")

# AUC
tree_auc <- performance(tree_scores, "auc")
tree_auc2<- as.numeric(tree_auc@y.values)
tree_auc2 # Area Under the Curve
```

We can also look deep into the classfication tree and see how the tree make its decompositions 

```{r}
tree1 <- rpart(training.y~., training, cp = 0.04216216)
rpart.plot(tree1) 

```

## Variable Importance
We will see the most important variable and confirm if the top 3 variables are the same as the decesion tree graph
```{r}
plot(varImp(clasmodel))
```

From the graph above we can see that the 3 top most important variables that make restaurants get 3 stars or more on Yelp are checking peoples coats, having an outdoor seating, and  dogs allowed

To see if this is true we can analyze the 2 variables visually 
```{r message=FALSE}

training$CoatCheck<-revalue(training$CoatCheck, c("1"="Has Coat Check", "0"="No Coat Check"))

training$OutdoorSeating<-revalue(training$OutdoorSeating, c("1"="Has Outdoor Seating", "0"="No Outdoor Seating"))

training$DogsAllowed<-revalue(training$DogsAllowed, c("1"="Dogs Are Allowed", "0"="Dogs Not Allowed"))
```

```{r}
p1<-ggplot(data = training) +
        geom_bar(aes(x = factor(CoatCheck), fill =  factor(training.y)), position = "fill",width = 0.3)+
        xlab("Restaurant")+
        ylab("Ratios")+
       labs(fill="CoatCheck")+ # Good (most low star resturants does not have valet, so it could be a good predictor)
 facet_wrap(~ factor(OutdoorSeating))
p1

```

The graph above shows that restaurant that has coat checks and outdoor seating is the most likely to have 3 stars or higher on Yelp


